A Container-Based Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-10-14 draft.tex
Title channged
Closes #26
Removed paragraph about credit cads
Closes #25

\title{EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms}

@@

We have mentioned several advantages of a cloud-native application for running
multi-population based algorithms, but there are in our experience, several
issues that make this approach more practical. % several issues that make it practical or useful instead? - JJ 
In general, cloud platforms have free-tiers    
for their services, and many offer academic discounts to students. But once we
pass to the pay-as-you-go tier, computing resources need to be
managed, and, where possible, its cost minimized.  First,
in many cases,  a credit-card is needed to guarantee the payment of the
resources consumed and someone responsible for assigning quotas and, more
importantly, special keys for using the cloud's API.  If these keys are
compromised or shared by their holders,  additional costs or administrative
procedures are in order. For those cases when a prototype platform is needed,
for instance, students developing a new algorithm variant or experimenting with
a published work, a container-based platform can be more practical. Container
technology enables researchers the local deployment of all the infrastructure
needed to run the experiments. Later, if needed, the same system could be
deployed to the cloud.

>>>>

\title{A Container-Based Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms}

@@

% We have mentioned several advantages of a cloud-native application for running
% multi-population based algorithms, but there are in our experience, several
% issues that make this approach more practical. % several issues that make it practical or useful instead? - JJ 
% In general, cloud platforms have free-tiers    
% for their services, and many offer academic discounts to students. But once we
% pass to the pay-as-you-go tier, computing resources need to be
% managed, and, where possible, its cost minimized.  First,
% in many cases,  a credit-card is needed to guarantee the payment of the
% resources consumed and someone responsible for assigning quotas and, more
% importantly, special keys for using the cloud's API.  If these keys are
% compromised or shared by their holders,  additional costs or administrative
% procedures are in order. For those cases when a prototype platform is needed,
% for instance, students developing a new algorithm variant or experimenting with
% a published work, a container-based platform can be more practical. Container
% technology enables researchers the local deployment of all the infrastructure
% needed to run the experiments. Later, if needed, the same system could be
% deployed to the cloud.
